Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-23 paper/ijcai/paper.tex
another comment
pass on RQ2

\Mar{-------------------- estou aqui}

In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
statements, since it is one of the main issues of dynamic slicing techniques. This
is particularly important because when \ds{} misses a faulty statement
means that it will not be in the diagnostic report and therefore has a negative
impact in the fault localization accuracy. Table~\ref{table:fsws} presents the
number of faults where at least one of the faulty statements appears in the
final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault,
we only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
of the highest faulty classes.

In Table~\ref{table:fsws}, we observe that for both scenarios ($k=5$ and $k=10$), \combpar{k}
finds the faulty statements faster than \sfl{}$^{k}$.
\sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas \combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e.,
\combpar{5} misses less $20$ ($7.7\%$) faults than \sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults where as \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10} misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$. There is also a significant difference within each technique. Generally, the majority of faulty statements are found on the $5$ highest ranked faulty classes. There are few cases where the faulty statements are only find if the approach considers the first $10$ highest ranked faulty classes \combpar{10} is the variant of our approach
that performs better \textbf{missing only 23 out of 260 (8.8\%) cases}.

@@

>>>>

%% For automated debugging that
%% means that it will not be in the diagnostic report and therefore has a negative
%% impact in the fault localization accuracy.

%% In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
%% statements, since it is one of the main issues of dynamic slicing techniques. This
%% is particularly important because when \ds{} misses a faulty statement

%% of both techniques, \sfl{}$^{k}$ and \combpar{k}

A fundamental issue of purely dynamic slicing techniques, critical
slicing in particular, is the risk of discarding faulty statements
(see Section~\ref{sec:slicing}). This research question evaluates the
practical impact of this conceptual issue. Table~\ref{table:fsws}
presents the number of faults where at least one of the faulty
statements appears in the final reports.\Mar{$\leftarrow$this seems a
  sensible choice that needs reasonable (to-the-point)
  justification. is there a rationale for this?  if not, was this
  choice used in other study? if yes, just say it was used and cite.}
More precisely, we look for faulty statements in the top 5 and 10 most
suspicious classes (as per the file ranking).

\Mar{CRITICAL: Sofia, I am really confused here. Is there a reason for
  why you chose not to show the proportion of cases where **DS** (not
  SFL(k) or \combpar{k}) includes the faulty statement? Wouldn't it be
  sufficient and simpler/clearer answering this question in terms of
  DS for k=5,10? (Note that the question is about DS.) On a similar
  note, considering this metric, I don't understand how SFL(k) can
  produce different result compared to \combpar{k}. I thought the
  difference in this case would only be the position in the
  ranking. This is counter-intuitive and needs a good explanation.}
Table~\ref{table:fsws} compares \sfl{}$^{k}$ and \combpar{k} with
respect to the metric number of cases where a faulty statement appears
in the ranking. Results show that \combpar{k} finds the faulty
statements \Fix{faster}\Mar{faster? chose another word.} than
\sfl{}$^{k}$.\Mar{I will revise the rest of this par. when I
  understand what is going on here...}  \sfl{}$^{5}$ finds $207$
($79.6\%$) faults whereas \combpar{5} finds $227$ ($87.3\%$) faults
for $k=5$, i.e., \combpar{5} misses $20$ ($7.7\%$) less faults
compared to \sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults
whereas \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e.,
\combpar{10} misses less $20$ ($7.7\%$) faults than
\sfl{}$^{10}$. There is also a significant difference within each
technique. Generally, the majority of faulty statements are found on
the $5$ highest ranked faulty classes. There are few cases where the
faulty statements are only found if the approach considers the first
$10$ highest ranked faulty classes \combpar{10} is the variant of our
approach that performs better \textbf{missing only 23 out of 260
  (8.8\%) cases}.

@@

\Mar{---------------------- I am here}
